discussion

### 2018-05-08 man/ms_3_discussion.Rmd
update

@@

El sitio del norte, ()

@@

Our results showed differences for greenness and tree-growth between northern and southern oak populations ().

>>>>

Our results showed differences for greenness and tree-growth between northern and southern oak populations (Table 3). Las poblaciones del norte, que presentan condiciones mas secas (Tabla 1), se vieron mas afectadas por los eventos de sequía. Así por ejemplo vimos que las anomalías estandarizadas de EVI fueron mas negativas en la población del norte durante la sequía de 2005 (mayor intensidad de browing en 2005 para el norte).

Con respecto al BAI, observamos 
Llama la atención que en el rear-edge de la distribución de la especie, en el sitio mas meridional dentro de este rear edge, y en la parte mas alta (estas parcelas están en el treeline de la especie en SN (en torno a 1900)), es donde encontramos mayores crecimientos. Parece que los robles estuvieran mejor en esta zona. Algunas reflexiones sobre esto:

A striking result is the difference for tree growth between southern sites (Figure 4). Despite these sites are very close to each other, we obtained higher values of BAI for the high-elevation site than for the low-elevation site.

The trees of CA-High site, which are located around 1900 m. a.s.l. and representing the upper limit of the treeline of the species in this southernmost location, showed higher BAI than those located at low-elevations sites (CA-Low and SJ). This is especially interesting for southern sites, which  are very close to each other.

In addition, despite southern sites are very close to each other, we obtained higher values of BAI for the high-elevation site than for the low-elevation site.

Algunos autores [@VicenteSerrano2014b] hablan de que las respuestas 
Growth and responses to drought are modulated by site conditions such as soil type, specific functional traits and the intensity of competition among neighbouring trees (Orwig & Abrams, 1997; McDowell et al., 2008; Linares et al., 2010; Pasho et al., 2011)

-----------

@@

@@
